How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-07 tse-paper/content.tex
Make links clickable
start on discussion draft, bit of rw moving

% TODO Caro cite guidelines
Our Google Scholar
search for variations ``build log'' returns more than 2.2 million results
(2020-03-15).
We therefore refined our search criterions for the four
different spelling possibilities of ``build log'' to exclude obvious
non-related works.
We explicitly decided to exclude systems
or event logs (see \Cref{sec:rw}).
This left us with 1,552 combined search results
(2020-03-15).
The full search queries are documented in our replication
package~\cite{brandt2020chunk-replication}.

@@

With these 256 remaining articles, we followed a backward snowball
sampling for related work. This meant that we added an article if referred in them in the context of log analysis. 
This added five papers (eight before
duplicate elimination) to our literature set, coming to a total of 261
articles.

@@

@@

\subsubsection{Build Logs}
Of the articles we surveyed, 30\% analyzed build logs produced by
Maven~\cite{maven2019website}, 16\% ones produced by Gradle % TODO: cite
and 10\% logs produced by Ant.
% TODO: cite
The distribution of supported build tools is shown in
\Cref{fig:litsur:log_producer}.
Only 7\% of the proposed methods claimed to be language-agnostic, while
several described they are covering multiple source build tools.
The majority of articles (42\%) targeted logs from a source which was not
targeted by any second article.

@@

\subsection{Discussion}
various researchers analyzing build logs to support their research,
tools developed to help developers % TODO: {motivational reference}.

@@

\subsection{Build Failures in CI}
Various researchers studied why CI builds fail and into the impact of
build failures on the development workflow.

@@

\subsection{System Log Analysis}
\label{sec:log-analysis}
A related field of log processing is the processing of system log
files produced during runtime.
A main difference between build logs
and system logs is that system logs are fundamentally structured
through events.
Each line in a log file represents one event with a
set of fields: timestamp, verbosity level and raw message
content~\cite{he2017towards}.
Figure \ref{lst:system-log} shows
example lines from a system log.

\subsection{Program Synthesis by Example}
\label{sec:rw-prose}
% % \section){Information Extraction and Retrieval Techniques} The
% % techniques we investigate are based on existing methods of
% % Programming by Example.%, information extraction and information
% % retrieval.
% This section presents different Programming by Example
% % resources surrounding the PROSE library.
% We explain its generic
% % program synthesis algorithm and how PROSE synthesizes text
% % extraction programs, the foundation of PBE\@.

@@

\section{Chunk Retrieval Techniques}
\label{sec:techniques}
% TODO: rework! extend / relate to further techniques
This section introduces key concepts of the three chunk retrieval
techniques we study in this article, namely program synthesis by
example (PBE), common text similarity (CTS), and keyword search (KWS).
We use these techniques to extract text chunks from build logs that
represent a specific, targeted information.

@@

% TODO: we could add more techniques from the lit.
survey here

>>>>

% TODO Caro cite guidelines
Our Google Scholar
search for variations ``build log'' returns more than 2.2 million results
(2020-03-15).
We therefore refined our search criterions for the four
different spelling possibilities of ``build log'' to exclude obvious
non-related works.
We explicitly decided to exclude systems
or event logs (see \Cref{sec:system-log-analysis}).
This left us with 1,552 combined search results
(2020-03-15).
The full search queries are documented in our replication
package~\cite{brandt2020chunk-replication}.

@@

With these 256 remaining articles, we followed a backward snowball
sampling for related work.
This meant that we added an article if referred in them in the context
of log analysis.

This added five papers (eight before
duplicate elimination) to our literature set, coming to a total of 261
articles.

@@

\subsection{Distinction from System Log Analysis}
\label{sec:system-log-analysis}
A related field of build log analysis is the processing of system log
files produced during runtime.
A main difference between build logs
and system logs is that system logs are fundamentally structured
through events.
Each line in a log file represents one event with a
set of fields: timestamp, verbosity level and raw message
content~\cite{he2017towards}.
Figure \ref{lst:system-log} shows
example lines from a system log.

@@

\subsubsection{Build Logs}
The distribution of supported build tools is shown in
\Cref{fig:litsur:log_producer}.
Of the articles we surveyed, 30\% analyzed build logs produced by
Maven~\cite{maven2019website}, 16\% ones produced by Gradle % TODO: cite
and 10\% logs produced by Ant.
% TODO: cite
Sometimes this limitation to a specific build tool is motivated by
% TODO: PIT tool, often: much variety in log format only time for
one parser

Only 7\% of the proposed methods claimed to be language-agnostic, while
several described they are covering multiple source build tools.
The majority of articles (42\%) targeted logs from a source which was not
targeted by any second article.

@@

\subsection{Discussion}
Our literature survey sheds light on how build log analysis is used within
computer science research.
We saw that various researchers process build logs to support their
research, often because the logs provide more or the necessary information
to the researchers.
% TODO cite 'Autmoated localization for unreproducible builds
Automated approaches are necessary as many studies target a large
number of
builds.
Most of the articles which explicitly mention a manual analysis of
the logs
only restrict their work to few logs or take a ``representative sample to
make manual analysis feasible''.
% TODO cite: a study of build inflation in 30 mil CPAN builds

@@

% TODO Caro: integrate as anecdotes in lit results
\subsection{Build Failures in CI}
Various researchers studied why CI builds fail and into the impact of
build failures on the development workflow.

@@

% TODO: Caro: integrate into pbe description
\subsection{Program Synthesis by Example}
\label{sec:rw-prose}
% % \section){Information Extraction and Retrieval Techniques} The
% % techniques we investigate are based on existing methods of
% % Programming by Example.%, information extraction and information
% % retrieval.
% This section presents different Programming by Example
% % resources surrounding the PROSE library.
% We explain its generic
% % program synthesis algorithm and how PROSE synthesizes text
% % extraction programs, the foundation of PBE\@.

@@

\section{Chunk Retrieval Techniques}
\label{sec:techniques}
% TODO: rework! extend / relate to further techniques
% (should follow from discussion)
This section introduces key concepts of the three chunk retrieval
techniques we study in this article, namely program synthesis by
example (PBE), common text similarity (CTS), and keyword search (KWS).
We use these techniques to extract text chunks from build logs that
represent a specific, targeted information.

@@

% TODO: we could add more techniques from the lit.
% survey here
